Gravitational Lens Modeling of Flux Ratio Anomalous System B1555+375

### 2015-01-14 papers/B1555_EdgeOn/B1555_letter.tex
new references and few type correction

\section{Introduction}
To understand substructions and mass distribution within dark matter haloes, observations in Local Group bring the first view of mass profile on small scale by searching satellite galaxies directly. However, concordant cold dark matter cosmology predicts more substructures in numerical simulations than in observation results around our Milky Way. This discrepency arises the famous ``missing satellite'' problem. Searching more satellite galaxies beyond Local Group is definite one of the keys to solve this discrepency, though, in approaches with huge differences from people used to do in Local Group. Most satellite galaxies are faint, which are extremely hard to directly detect in the system beyond Milky Way. Futhermore, some low-mass dark matter subhaloes are considered to be too small to contain dwarf galaxies. These factors make gravitational effects be powerful and promising tools in the substructure searching.\\   
Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness due to perturbations in gravitational potential. Little perturbation from substructures (mass range?) is sufficent to bring flux ratio anomalies in strong lensed systems. In the observational view, radio observation is the best way to probe these flux ratio anomalous systems because it doesn't have severe extinction issue like in optical or infrared band. Also, most radio lensed images are point sources which are easier to model. \\
On the other hand, results from numerical simulation haven't reach a concise conclusion on the cause of flux ratio anomaly. There are other possiblities can give rise to flux ratio anomaly. Before gathering any satistics or serious analysis, we must fully consider those non-substructure effects. Otherwise it could affect the estimation of substructure mass and even give false signal when searching possible satellite candidates. Among those non-substructure effects, we are interested in the gravitational effect caused by structure of lens galaxy itself. Thus, infrared image with high spatial resolution is essential in our study.\\
The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lesing systems. We obtain high-resoltion images from Keck adaptive optics(AO) Hubble Space Telescope(HST) observations. In the latest SHARP imaging, we found clear edge-on disk within some known flux ratio anomalous lenses. We model one system, B1555+375, with a center bulge and an edge-on disk, intending to probe the possibility of that structure from lens galaxy can cause flux ratio anomaly. We present the latest SHARP data in part 2, lens model of B1555 in part 3, and discussion in part 4.

>>>>

\section{Introduction}
To understand substructions and mass distribution within dark matter haloes, observations in Local Group bring the first view of mass profile on small scale by searching satellite galaxies directly. However, concordant cold dark matter cosmology predicts more substructures in numerical simulations than in observation results around our Milky Way. This discrepency arises the famous ``missing satellite'' problem \citep{Klypin1999}. Searching more satellite galaxies beyond Local Group is definite one of the keys to solve this discrepency, though, in approaches with huge differences from people used to do in Local Group. Most satellite galaxies are faint, which are extremely hard to directly detect in the system beyond Milky Way. Futhermore, some low-mass dark matter subhaloes are considered to be too small to contain dwarf galaxies. These factors make gravitational effects be powerful and promising tools in the substructure searching.\\   
Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness due to perturbations in gravitational potential. Little perturbation from substructures (mass range?) is sufficent to bring flux ratio anomalies in strong lensed systems. In the observational view, radio observation is the best way to probe these flux ratio anomalous systems because it doesn't have severe extinction issue like in optical or infrared band. Also, most radio lensed images are point sources which are easier to model. \\
On the other hand, numerical simulations on structure formation haven't reach a concise conclusion on the cause of flux ratio anomaly. There are other possiblities can give rise to flux ratio anomaly. Before gathering any satistics or serious analysis, we must fully consider those non-substructure effects. Otherwise it could affect the estimation of substructure mass and even give false signal when searching possible satellite candidates. Among those non-substructure effects, we are interested in the gravitational effect caused by structure of lens galaxy itself. Thus, infrared image with high spatial resolution is essential in our study.\\
The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lensing systems \citep{SHARP12}. We obtain high-resoltion images from Keck adaptive optics(AO) and Hubble Space Telescope(HST) observations. In the latest SHARP imaging, we found clear edge-on disk within some known flux ratio anomalous lenses. We model one system, B1555+375, with a center bulge and an edge-on disk, intending to probe the possibility of that structure from lens galaxy can cause flux ratio anomaly. We present the latest SHARP data in part 2, lens model of B1555 in part 3, and discussion in part 4.
